Timeliness of security updates for Android

### 2014-08-11 security_scoring.tex
Qualify operator scores

\daTabSecScoresoperator
We also analysed different operators, for the \daNumSigOperators\ operators with a significant presence in our data Table~\ref{tab:sec_operator} shows the results \daSecScoreBestoperator\ (\daSecScoreBestoperatorScore\ / 10) doing best and \daSecScoreWorstoperator\ (\daSecScoreWorstoperatorScore\ / 10) doing worst.

>>>>

\daTabSecScoresoperator
We also analysed different operators, for the \daNumSigOperators\ operators with a significant presence in our data Table~\ref{tab:sec_operator} shows the results \daSecScoreBestoperator\ (\daSecScoreBestoperatorScore\ / 10) doing best and \daSecScoreWorstoperator\ (\daSecScoreWorstoperatorScore\ / 10) doing worst.
However the score of an operator is affected by the manufacturers of the devices which are in use on it's network.
This is in turn affected by both what devices an operator offers to users and on which devices users choose.
Hence having a worse score does not necessarily mean that an operator is worse, it could be that its users all pick phones from a worse manufacturer, for example because they were cheaper.
